---
title: "Quora Duplicate Questions"
author: "Tinus Cloete"
date: "31 March 2017"
output: html_document
---

## Overview

This is a competition on Kaggle where the aim is to identify duplicate questions within in a Quora dataset of questions. 
This is done in order to make it easier to find the correct answers for a given question on the internet.

## Data

The data can be found in the following location: [Quora Question Data](https://www.kaggle.com/c/quora-question-pairs/data)

Lets start off by loading the data into a dataframe

```{r setup, include = FALSE}
library(tidyverse)
library(tidytext)
```

```{r}
train <- read_csv("Data/train.csv")

head(train)
```

So the structure of the data is the following:

Column | Description
------ | ----------------------------------------------------------------
id:    | the id of a training set question pair
qid1:  | unique id of question 1 (only available in train.csv)
qid2:  | unique id of question 2 (only available in train.csv)
question1: | the full text of question 1
question2: | the full text of question 2
is_duplicate: | the target variable, 1 if question1 and question2 have essentially the same meaning, and 0 otherwise.

Let see what the distribution is over the different numerical columns:

```{r}

summary(train)

```

So overall about 37% of the questions in the training data were identified as duplicates. That is actually quite high!
The credibility is also decent with over 404 000 question pairs.

The next step is the cleaning of the text in the questions.

```{r}

questions <- train %>% 
             select(id, qid=qid1, question=question1) %>% 
             bind_rows(train %>% select(id, qid=qid2, question=question2)) %>% 
             arrange(id, qid)

tidy_questions <- questions %>% 
                  unnest_tokens(word, question)

tidy_questions %>% filter(id == 0)

```


